---
title: "R Notebook"
output: html_notebook
---

First we install required libraries - 

```{r, warning=FALSE}
## Installing packages and setting working directory

library(dplyr)
library(ggplot2)
library(lubridate)
library(skimr)


```

Next we read data

```{r, warning=FALSE}
house <- read.csv('kc_house_data_rik.csv') # this is the renamed kc_house_data (1) uploaded by Rik
summary(house)
```

We notice that the data needs a certain amount of cleaning (e.g. date variable) and we also derive a few metrics, namely 

```{r, warning = FALSE}
## Removing lat and long
house_new <- house %>% select(-c(lat, long))

# DERIVING NEW METRICS

## Total sqft
house_new <- house_new %>% mutate(total_sqft = sqft_living + sqft_lot + sqft_basement,
                          total_sqft15 = sqft_living15 + sqft_lot15 + sqft_basement)

## Change in sqft (after renovation)
house_new <- house_new %>% mutate(change_in_sqft = total_sqft15 - total_sqft)

## House newness
house_new <- house_new %>% mutate(year_sold = year(ymd(substr(house_new$date, 1,8))))
house_new <- house_new %>% mutate(newness = year_sold - pmax(yr_built, yr_renovated))

## Bed to bath ratio
house_new <- house_new %>% mutate(bed_bath_ratio = bedrooms/bathrooms)

## Cleaning date value
house_new$date <- gsub('T000000', '', house_new$date)
house_new <- house_new %>% mutate(date_new = ymd(date))
house_new <- house_new %>% mutate(year_sold = year(date_new))

## Average floor size

house_new <- house_new %>% mutate(area_floor_ratio = sqft_living/floors, area_floor_ratio_15 = sqft_living15/floors)
house_new <- house_new %>% mutate(area_floor_change = area_floor_ratio_15 - area_floor_ratio)

colnames(house_new)
```

## Descriptive stats

```{r}
## Relation between grade and living area
#ggplot(house) + aes(x=as.factor(grade), y = sqft_living) + geom_boxplot()
#ggplot(house) + aes(x=as.factor(grade), y = price) + geom_boxplot()

# Relation between 
#ggplot(house) + aes(x=as.factor(waterfront), y = price) + geom_boxplot()
#house_new$bedrooms = as.factor(house_new$bedrooms)
#house_new$bathrooms = as.factor(house_new$bathrooms)
summary(house_new)
```


##descriptive analysis
```{r}
house_new %>% ggplot(aes(x=price)) + geom_histogram(bins = 50)
```


#bedroom 
```{r}
unique(house_new$bedrooms)
#summary(lm(house_new$price~as.factor(house_new$bedrooms)))
bedroom.aov = aov(house_new$price~as.factor(house_new$bedrooms),data = house_new)
summary(bedroom.aov)
```
```{r}
house_new %>% ggplot(aes(bedrooms,price,group = bedrooms))+geom_boxplot()+xlim(0,20)
```

Tukey
```{r}
aa = TukeyHSD(bedroom.aov,conf.level = .9)
aa = aa$`as.factor(house_new$bedrooms)`
aa[,4][aa[,4]<=0.05]
```

#bathroom
```{r}
unique(house_new$bathrooms)
bathroom.aov = aov(house_new$price~as.factor(house_new$bathrooms),data = house_new)
summary(bathroom.aov)
```

```{r}
house_new %>% ggplot(aes(bathrooms,price,group = bathrooms))+geom_boxplot()+xlim(0,10)
```


```{r}
house_new %>% ggplot(aes(bathrooms,price,group = bedrooms))+geom_boxplot()+xlim(0,7)
```


```{r}
aa = TukeyHSD(bathroom.aov,conf.level = .9)
aa = aa$`as.factor(house_new$bathrooms)`
aa[,4][aa[,4]<=0.05]

```


#waterfront
```{r}
unique(house_new$waterfront)
waterfront.aov = aov(house_new$price~as.factor(house_new$waterfront),data = house_new)
summary(waterfront.aov)
```

```{r}
house_new %>% ggplot(aes(waterfront,price,group = waterfront))+geom_boxplot()+xlim(-1,2)
```

#floor

```{r}
unique(house_new$floors)
floor.aov = aov(house_new$price~as.factor(house_new$floors),data = house_new)
summary(floor.aov)
```

```{r}
house_new %>% ggplot(aes(floors,price,group = floors))+geom_boxplot()+xlim(0,5)
```

```{r}
aa = TukeyHSD(floor.aov,conf.level = .9)
aa = aa$`as.factor(house_new$floors)`
aa[,4][aa[,4]<=0.05]
```


#condition
```{r}
unique(house_new$condition)
condition.aov = aov(house_new$price~as.factor(house_new$condition),data = house_new)
summary(condition.aov)
```

```{r}
house_new %>% ggplot(aes(condition,price,group = condition))+geom_boxplot()+xlim(-0.05,5.5)
```

```{r}
aa = TukeyHSD(condition.aov,conf.level = .9)
aa = aa$`as.factor(house_new$condition)`
aa[,4][aa[,4]<=0.05]
```
#grade
```{r}
unique(house_new$grade)
grade.aov = aov(house_new$price~as.factor(house_new$grade),data = house_new)
summary(grade.aov)
```
```{r}
house_new %>% ggplot(aes(grade,price,group = grade))+geom_boxplot()+xlim(-0.05,13)
```


#newness

```{r}
lm = lm(price~newness,data = house_new)
summary(lm)
plot(lm)
```

#Zipcode
```{r}
house_new$zipcode = as.character(house_new$zipcode)
house_new %>% ggplot(aes(zipcode,price))+geom_boxplot()
```
```{r}
unique(house_new$grade)
zipcode.aov = aov(house_new$price~as.factor(house_new$grade),data = house_new)
summary(zipcode.aov)
```


#TODO: Zipcode->City

##Modeling


```{r}
lm6 = lm(price~newness+sqft_above+sqft_basement+total_sqft+bedrooms+bathrooms+as.factor(waterfront)+as.factor(grade)+as.factor(zipcode),data = house_new)
summary(lm6)
anova(lm6)
```


#remove total_sqft(ok)
```{r}
lm7 = lm(price~newness+sqft_above+sqft_basement+as.factor(bedrooms)+as.factor(bathrooms)+as.factor(waterfront)+as.factor(grade)+as.factor(zipcode),data = house_new)
summary(lm7)
```

#remove newness (ok)
```{r}
lm8 = lm(price~sqft_above+sqft_basement+as.factor(bedrooms)+as.factor(bathrooms)+as.factor(waterfront)+as.factor(grade)+as.factor(zipcode),data = house_new)
summary(lm8)
```

#remove bathroom (Nope)
```{r}
lm9 = lm(price~sqft_above+sqft_basement+as.factor(bedrooms)+as.factor(waterfront)+as.factor(grade)+as.factor(zipcode),data = house_new)
summary(lm9)
```

#remove bedroom (ok)
```{r}
lm10 = lm(price~sqft_above+sqft_basement+as.factor(bedrooms)+as.factor(waterfront)+as.factor(grade)+as.factor(zipcode),data = house_new)
summary(lm10)
```

#remove waterfront (Nope)
```{r}
lm11 = lm(price~sqft_above+sqft_basement+as.factor(bathrooms)+as.factor(grade)+as.factor(zipcode),data = house_new)
summary(lm11)
```



